Did COVID-19 Induce A Strenuous Effect on the 311 Non-Emergency Services System?

### 2022-07-17 draft_v2.Rmd
robustness checks

```{r}
# create data for request level reg
dat_reg = dat %>% 
  filter(allcovid==0) %>%
  left_join(zip_covid_311) %>% 
  mutate(after = as.numeric(season == "COVID-warm"),
         did = n_allcovid*after
         ) %>%  
  left_join(dat911, by=c("CREATEMO" = "month","CREATEYR" = "year")) %>%
  left_join(datgov, by=c("CREATEMO" = "month","CREATEYR" = "year"))

@@

```{r}
#ols 
reg_ols = lm(data= dat_reg, DAYTOCLOSE~did + n_allcovid + after)
#fe: rate + after
reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+after ))
#fe: rate + date(year-month)
reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+factor(date) ))
#fe: rate + date(year-month)
reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~did|factor(NEIGH)+factor(date) ))

@@

@@

#combine reg 
screenreg(list(reg_fe_11, reg_fe_12,reg_fe_13,reg_fe_14,reg_fe_15), 
          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("Sidewalks / Curbs / Ditch", "Signs","Storm Water / Sewer","Streets / Roadways / Alleys","Trash / Recycling"),
          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
          )

>>>>

```{r}
# create data for request level reg
dat_reg = dat %>% 
  filter(allcovid==0) %>%
  left_join(zip_covid_311) %>% 
  mutate(after = as.numeric(season == "COVID-warm"),
         did = n_allcovid*after,
         ) %>%  
  left_join(dat911, by=c("CREATEMO" = "month","CREATEYR" = "year")) %>%
  left_join(datgov, by=c("CREATEMO" = "month","CREATEYR" = "year"))

@@

Main results

@@

By Categories

@@

#combine reg 
screenreg(list(reg_fe_11, reg_fe_12,reg_fe_13,reg_fe_14,reg_fe_15), 
          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("Sidewalks / Curbs / Ditch", "Signs","Storm Water / Sewer","Streets / Roadways / Alleys","Trash / Recycling"),
          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees"))
```

Robustness Check

Fixed Effects 
```{r}
#ols 
reg_ols = lm(data= dat_reg, DAYTOCLOSE~did + n_allcovid + after)
#fe: rate + after
reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+after ))
#fe: rate + date(year-month)
reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~did|n_allcovid+factor(date) ))
#fe: rate + date(year-month)
reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~did|factor(NEIGH)+factor(date) ))

test for difference in pre-period time trends

```{r}
summary( felm(data= dat_reg, DAYTOCLOSE~n_allcovid:relevel(factor(date),ref=12)|ZIP+factor(date) ))
```

Placebo test - time:
move treatment time to before treatment, expect not significant

```{r}
#create time placebo
dat_reg = dat_reg %>% 
  mutate(
         placebo_after = as.numeric(CREATEYR==2020),
         placebo_did = n_allcovid*placebo_after,
         )

#fe: rate + after
reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~placebo_did|n_allcovid+placebo_after ))
#fe: 911
reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~placebo_did+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+placebo_after ))
#fe: gov employees
reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~placebo_did+empgov|n_allcovid+placebo_after ))
#fe: 911 + gov employees
reg_fe_d = (felm(data = dat_reg,DAYTOCLOSE~placebo_did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+placebo_after ))

Placebo test - treatment:
move treatment effect randomly, expect not significant

```{r}
#create time placebo
set.seed(0)
dat_reg = dat_reg %>% 
  mutate(
         placebo_after = as.numeric(CREATEYR==2020),
         placebo_allcovid = sample(n_allcovid,size = nrow(dat_reg)),
         placebo_did2 = placebo_allcovid*after,
         )

#fe: rate + after
reg_fe_a = (felm(data = dat_reg,DAYTOCLOSE~placebo_did2|n_allcovid+after ))
#fe: 911
reg_fe_b = (felm(data = dat_reg,DAYTOCLOSE~placebo_did2+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
#fe: gov employees
reg_fe_c = (felm(data = dat_reg,DAYTOCLOSE~placebo_did2+empgov|n_allcovid+after ))
#fe: 911 + gov employees
reg_fe_d = (felm(data = dat_reg,DAYTOCLOSE~placebo_did2+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
